Full title of the paper (Capitalized)

### 2022-03-07 Paper_Draft1/Draft1.tex
knit test

\begin{longtable}[]{@{}lll@{}}
\caption{This is a table caption. Tables should be placed in the main
text near to the first time they are
cited.\label{tab:mytable}}\tabularnewline
\toprule
Title 1 & Title 2 & Title 3 \\
\midrule
\endfirsthead
\toprule
Title 1 & Title 2 & Title 3 \\
\midrule
\endhead
entry 1 & data & data \\
entry 2 & data & data \\
\bottomrule
\end{longtable}

@@

Citing book reference \citet{gujer_systems_2008} Citing reference with
parentheses \citep{leutnant_stormwater_2016}

\citet{hardin2015data} advocated for more data science in statistics
curricula.

>>>>

\begin{longtable}[]{@{}lll@{}}
\caption{This is a table caption. Tables should be placed in the main
text near to the first time they are
cited.\label{tab:mytable}}\tabularnewline
\toprule
Title 1 & Title 2 & Title 3\tabularnewline
\midrule
\endfirsthead
\toprule
Title 1 & Title 2 & Title 3\tabularnewline
\midrule
\endhead
entry 1 & data & data\tabularnewline
entry 2 & data & data\tabularnewline
\bottomrule
\end{longtable}

@@

\citet{angwin2016machine} \citet{bao2021s} \citet{barocas2017fairness}
\citet{baumer2017texts} \citet{equivant_response_2018}
\citet{gebru2021datasheets} \citet{hardin2015data}
\citet{james2013introduction} \citet{knight2020automated}
\citet{kypraiou_what_2021} \citet{larson2016technical}
\citet{larson2016we} \citet{noauthor_ai_nodate}
\citet{noauthor_aif360datasetscompasdataset_2018}
\citet{noauthor_trusted-ai_360}
\citet{noauthor_propublicacompas-analysis_2022}
\citet{noauthor_womenthetable_nodate} \citet{vartan_1st_2022}
